\gettitle

### 2019-11-02 assignment1/submission1.tex
Change 1.2 to account for clock-skew

\section*{2 System Models}
\subsection*{a)}
\begin{itemize}
	\item No message is lost
	\item The maximal possible delay is known
\end{itemize}
\subsection*{b)}
\subsubsection*{i.}
Every process i sends its own messages at time $ i * \delta t$:
t\textsubscript{i}\textsuperscript{send}(m) = $ i * \delta t $
The tranmission of a given message is not longer than $ \delta $t, so if a process i starts sending after i * $ \delta $t every process with a lower id has allready finished and all processes know there messages.
\subsubsection*{ii.}
The worst-case is n * $ \delta $t as $ \delta $t is reserved for every prozess as time to send und $ \delta $t is the loangest time a prozess needs for transmitting a message

>>>>

\section*{2 System Models}
\subsection*{a)}
\begin{itemize}
	\item No message is lost
	\item The maximum possible delay is known
	\item There is a limited amount of clock skew between the processes
\end{itemize}
\subsection*{b)}
\subsubsection*{i.}
Assuming a limited clock skew of \(\delta c\) between the processes, the process \(P_i\) sends a broadcast message \(2 * \delta c + \delta t\) time units after receiving \(i - 1\) messages.
This allows for instant delivery to a process skewed by the maximum amount of time ''forwards'' while keeping the order of messages intact when sending the message even with the maximum delay \(\delta t\) to a process skewed by the maximum amount of time ''backwards''.
\subsubsection*{ii.}
In the worst case, the synchronization protocol takes \(2n (\delta t + \delta c) + 2\delta c\) time units.
This assumes that all messages take the maximum possible amount of time to deliver, namely \(n delta t\) overall, with clock skew cancelling itself out across all processes.
Adding the wait-time for each process \(n(\delta t + 2\delta c)\) yields \(2n (\delta t + \delta c)\).
The final component is assuming the maximum clock skew between \(P_1 \text{ and } P_n\).
